---
title: "ECON 613 Aassignment 1"
author: Nond Prueksiri
output: pdf_document
---
\fontsize{10}{10}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing Data
```{r importing data}
  rm(list = ls())

  datstu <- read.csv("C:/Users/nprue/Desktop/econ613/datstu.csv")
  datsss <- read.csv("C:/Users/nprue/Desktop/econ613/datsss.csv")
  datjss <- read.csv("C:/Users/nprue/Desktop/econ613/datjss.csv")
```

## Excercise 1  Missing Data
- Number of Students
```{r no. of students}
  # Assuming each obervation represents each students
    length(unique(datstu$X))
```

- Number of Schools
```{r no. of schools}
  # Eliminate missing data
    datsssA <- datsss[!(is.na(datsss$schoolname)
                        |is.na(datsss$schoolcode)
                        |is.na(datsss$sssdistrict)
                        |is.na(datsss$ssslong)
                        |is.na(datsss$ssslat)),]
  # Eliminate duplicated schoolcode
    datsssB <- datsssA[!(duplicated(datsssA$schoolcode)),]
  # Report the number of schools
    length(datsssB$schoolcode)
```

- Number of programs
``` {r no. of programs}
  # Clean out missing programs
    datstuA <- datstu[!(is.na(datstu[11])
                       |is.na(datstu[12]) 
                       |is.na(datstu[13])
                       |is.na(datstu[14]) 
                       |is.na(datstu[15])
                       |is.na(datstu[16])),]
  # Report the number of programs
    length(unique(unlist(datstuA[,11:16])))
```

- Number of Choices (School, Program)
``` {r no. of choices}

  # Clean out missing school choices
    datstuB <- datstuA[!(is.na(datstuA[5])
                       |is.na(datstuA[6]) 
                       |is.na(datstuA[7])
                       |is.na(datstuA[8]) 
                       |is.na(datstuA[9])
                       |is.na(datstuA[10])),]

  # Combine school and program choices, keep only unique ones
    datstuB$choice1 <- paste(datstuB[,5],"-" , datstuB[,11])
    datstuB$choice2 <- paste(datstuB[,6],"-" , datstuB[,12])
    datstuB$choice3 <- paste(datstuB[,7],"-" , datstuB[,13])
    datstuB$choice4 <- paste(datstuB[,8],"-" , datstuB[,14])
    datstuB$choice5 <- paste(datstuB[,9],"-" , datstuB[,15])
    datstuB$choice6 <- paste(datstuB[,10],"-" , datstuB[,16])
  
  # Report the number of program choices (school, program)
    length(unique(unlist(datstuB[,19:24])))
```

- Missing Test Score
``` {r missing test score}
  # Create missing score vector
  missing <- datstu[is.na(datstu$score), ]
  length(missing$X)
```

- Number of students applying to the same school

Who has the repeated schools with in her choices....
``` {r same school}
  # Create a logical column (TRUE = at least has one repeat) 
  datstu$sameschool <-  (datstu$schoolcode1 == datstu$schoolcode2 
                      | datstu$schoolcode1 == datstu$schoolcode3 
                      | datstu$schoolcode1 == datstu$schoolcode4 
                      | datstu$schoolcode1 == datstu$schoolcode5 
                      | datstu$schoolcode2 == datstu$schoolcode3 
                      | datstu$schoolcode2 == datstu$schoolcode4 
                      | datstu$schoolcode2 == datstu$schoolcode5 
                      | datstu$schoolcode3 == datstu$schoolcode4 
                      | datstu$schoolcode3 == datstu$schoolcode5 
                      | datstu$schoolcode4 == datstu$schoolcode5)

  # Return the number
  nrow(datstu[datstu$sameschool == 'TRUE',])
``` 
  
Who has applied to only one school....
``` {r same school 2} 
  # Create a logical column (TRUE = only one school) 
  datstu$oneschool <- (is.na(datstu$schoolcode2) 
                      | datstu$schoolcode1 == datstu$schoolcode2) & (is.na(datstu$schoolcode3) 
                      | datstu$schoolcode1 == datstu$schoolcode3) & (is.na(datstu$schoolcode4) 
                      | datstu$schoolcode1 == datstu$schoolcode4) & (is.na(datstu$schoolcode5) 
                      | datstu$schoolcode1 == datstu$schoolcode5) & (is.na(datstu$schoolcode6) 
                      | datstu$schoolcode1 == datstu$schoolcode6)
  
  # Return the number
  nrow(datstu[datstu$oneschool == 'TRUE',])
```

- Number of students applying less than 6 choices
``` {r less than 6} 
  # Create a logical column (TRUE = below 6 choices) 
  datstu$belowSix <- (is.na(datstu$schoolcode1) | is.na(datstu$schoolcode2) | is.na(datstu$schoolcode3) 
                    |is.na(datstu$schoolcode4) | is.na(datstu$schoolcode5) | is.na(datstu$schoolcode6))

  # Return the number
  nrow(datstu[datstu$belowSix == 'TRUE',])
```

## Excercise 2 Data

```{r create data , echo=TRUE, include = TRUE}
    library(data.table)
  # Remove unused data
  rm(datstuA, datstuB, datsssA, datsssB, missing)
  datadmit <- datstu[ , 1:18]
  # Remove invalid rankplace, i.e., NA and 99  
  datadmit <- datadmit[!(is.na(datadmit$rankplace) | datadmit$rankplace == 99), ]
    
  # Create variable "schoolcode" = school that a student is placed into
  datadmit$schoolcode <- NA
  datadmit$schoolcode[which(datadmit$rankplace == 1)] <- datadmit$schoolcode1[which(datadmit$rankplace == 1)]
  datadmit$schoolcode[which(datadmit$rankplace == 2)] <- datadmit$schoolcode2[which(datadmit$rankplace == 2)]
  datadmit$schoolcode[which(datadmit$rankplace == 3)] <- datadmit$schoolcode3[which(datadmit$rankplace == 3)]
  datadmit$schoolcode[which(datadmit$rankplace == 4)] <- datadmit$schoolcode4[which(datadmit$rankplace == 4)]
  datadmit$schoolcode[which(datadmit$rankplace == 5)] <- datadmit$schoolcode5[which(datadmit$rankplace == 5)]
  datadmit$schoolcode[which(datadmit$rankplace == 6)] <- datadmit$schoolcode6[which(datadmit$rankplace == 6)]
  
  # Create variable "adprog" = program that a student is placed into
    datadmit$adprog <- NA
    datadmit$adprog[which(datadmit$rankplace == 1)] <- as.character(datadmit$choicepgm1[which(datadmit$rankplace == 1)])
    datadmit$adprog[which(datadmit$rankplace == 2)] <- as.character(datadmit$choicepgm2[which(datadmit$rankplace == 2)])
    datadmit$adprog[which(datadmit$rankplace == 3)] <- as.character(datadmit$choicepgm3[which(datadmit$rankplace == 3)])
    datadmit$adprog[which(datadmit$rankplace == 4)] <- as.character(datadmit$choicepgm4[which(datadmit$rankplace == 4)])
    datadmit$adprog[which(datadmit$rankplace == 5)] <- as.character(datadmit$choicepgm5[which(datadmit$rankplace == 5)])
    datadmit$adprog[which(datadmit$rankplace == 6)] <- as.character(datadmit$choicepgm6[which(datadmit$rankplace == 6)])
  

  # Eliminate missing data
    datsss <- datsss[!(is.na(datsss$schoolname)
                        |is.na(datsss$schoolcode)
                        |is.na(datsss$sssdistrict)
                        |is.na(datsss$ssslong)
                        |is.na(datsss$ssslat)),]
    
  # Eliminate duplicated schoolcode
    datsss <- datsss[!(duplicated(datsss$schoolcode)),]
  
  # Merge with datsss for sssdistrict, ssslong, ssslat by schoolcode
   ssdat <- merge(datadmit,datsss, by = "schoolcode", all.x = TRUE)
  
  # Create variable size, quality, size
  size <- rep(1,nrow(ssdat))
  ssdat <- data.table(ssdat)
  ssdat <- ssdat[, list(quality=mean(score), cutoff=min(score), size = sum(size)), by=c("schoolcode","adprog", "schoolname", "sssdistrict","ssslong","ssslat")]
  
  # Here is the data requied by the exercise
  summary(ssdat)
```

## Excercise 3 Distance

```{r distance, echo=TRUE, include=TRUE}

  # Prepare location of junior high schools
  jssloc <- datjss[,2:4]
  colnames(jssloc) <- c("jssdistrict","jsslong", "jsslat")

  # Merge JSS locations with choices(school,program) in the cleaned datstu data and drop 'NA' district
  datadmit <- merge(datadmit,jssloc, by = "jssdistrict", all.x = TRUE)
  datadmit <- datadmit[!is.na(datadmit$jsslat),]
  
  # Prepare location of high schools, collapse each school using unique()
  sssloc <- unique(ssdat[,c("schoolcode","ssslong", "ssslat")])
  
  # Merge location of high school,then, calculate the distance from given formular.
  # Repeat them by choice, i.e., choice1, ... , choice6
  colnames(sssloc) <- c("schoolcode1", "ssslong1", "ssslat1")
  datadmit <- merge(datadmit,sssloc, by ="schoolcode1", all.x = TRUE)
  datadmit <- datadmit[!is.na(datadmit$ssslat1),]
  dist1 <- sqrt(((69.172*(datadmit$ssslong1-datadmit$jsslong))*cos(datadmit$jsslat/57.3))^2 + (69.172*(datadmit$ssslat1-datadmit$jsslat))^2)
  datadmit <- cbind(datadmit, dist1) 
  
  colnames(sssloc) <- c("schoolcode2", "ssslong2", "ssslat2")
  datadmit <- merge(datadmit,sssloc, by ="schoolcode2", all.x = TRUE)
  datadmit <- datadmit[!is.na(datadmit$ssslat2),]
  dist2 <- sqrt(((69.172*(datadmit$ssslong2-datadmit$jsslong))*cos(datadmit$jsslat/57.3))^2 + (69.172*(datadmit$ssslat2-datadmit$jsslat))^2)
  datadmit <- cbind(datadmit, dist2) 
  
  colnames(sssloc) <- c("schoolcode3", "ssslong3", "ssslat3")
  datadmit <- merge(datadmit,sssloc, by ="schoolcode3", all.x = TRUE)
  datadmit <- datadmit[!is.na(datadmit$ssslat3),]
  dist3 <- sqrt(((69.172*(datadmit$ssslong3-datadmit$jsslong))*cos(datadmit$jsslat/57.3))^2 + (69.172*(datadmit$ssslat3-datadmit$jsslat))^2)
  datadmit <- cbind(datadmit, dist3) 
  
  colnames(sssloc) <- c("schoolcode4", "ssslong4", "ssslat4")
  datadmit <- merge(datadmit,sssloc, by ="schoolcode4", all.x = TRUE)
  datadmit <- datadmit[!is.na(datadmit$ssslat4),]
  dist4 <- sqrt(((69.172*(datadmit$ssslong4-datadmit$jsslong))*cos(datadmit$jsslat/57.3))^2 + (69.172*(datadmit$ssslat4-datadmit$jsslat))^2)
  datadmit <- cbind(datadmit, dist4) 
  
  colnames(sssloc) <- c("schoolcode5", "ssslong5", "ssslat5")
  datadmit <- merge(datadmit,sssloc, by ="schoolcode5", all.x = TRUE)
  datadmit <- datadmit[!is.na(datadmit$ssslat5),]
  dist5 <- sqrt(((69.172*(datadmit$ssslong5-datadmit$jsslong))*cos(datadmit$jsslat/57.3))^2 + (69.172*(datadmit$ssslat5-datadmit$jsslat))^2)
  datadmit <- cbind(datadmit, dist5) 
  
  colnames(sssloc) <- c("schoolcode6", "ssslong6", "ssslat6")
  datadmit <- merge(datadmit,sssloc, by ="schoolcode6", all.x = TRUE)
  datadmit <- datadmit[!is.na(datadmit$ssslat6),]
  dist6 <- sqrt(((69.172*(datadmit$ssslong6-datadmit$jsslong))*cos(datadmit$jsslat/57.3))^2 + (69.172*(datadmit$ssslat6-datadmit$jsslat))^2)
  datadmit <- cbind(datadmit, dist6) 
  
  # The Summary of required data
  summary(datadmit)
```

# Exercise 4 Descriptive Characteristics 

```{r discriptive, echo=TRUE, include=TRUE}
  # Remove unused values
  rm(dist1, dist2, dist3, dist4, dist5, dist6)
  
  # merge variable "cutoff" and "quality" to original data by choices [1:6]
  ssdat <- ssdat[, c("schoolcode","adprog","cutoff","quality")]  
  colnames(ssdat) <- c("schoolcode1","choicepgm1","cutoff1","quality1")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode1","choicepgm1"), all.x = TRUE)

  colnames(ssdat) <- c("schoolcode2","choicepgm2","cutoff2","quality2")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode2","choicepgm2"), all.x = TRUE)

  colnames(ssdat) <- c("schoolcode3","choicepgm3","cutoff3","quality3")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode3","choicepgm3"), all.x = TRUE)

  colnames(ssdat) <- c("schoolcode4","choicepgm4","cutoff4","quality4")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode4","choicepgm4"), all.x = TRUE)

  colnames(ssdat) <- c("schoolcode5","choicepgm5","cutoff5","quality5")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode5","choicepgm5"), all.x = TRUE)

  colnames(ssdat) <- c("schoolcode6","choicepgm6","cutoff6","quality6")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode6","choicepgm6"), all.x = TRUE)

# Calculate mean and sd of "Cutoff", "Quality" and "Distance"
result <- data.frame("Choice1", "Choice2", "Choice3", "Choice4", "Choice5", "Choice6")

xcutoff <- c(mean(as.numeric(datadmit$cutoff1), na.rm=TRUE),
             mean(as.numeric(datadmit$cutoff2), na.rm=TRUE),
             mean(as.numeric(datadmit$cutoff3), na.rm=TRUE),
             mean(as.numeric(datadmit$cutoff4), na.rm=TRUE),
             mean(as.numeric(datadmit$cutoff5), na.rm=TRUE),
             mean(as.numeric(datadmit$cutoff6), na.rm=TRUE)
             )

sdcutoff <- c(sd(as.numeric(datadmit$cutoff1), na.rm=TRUE),
             sd(as.numeric(datadmit$cutoff2), na.rm=TRUE),
             sd(as.numeric(datadmit$cutoff3), na.rm=TRUE),
             sd(as.numeric(datadmit$cutoff4), na.rm=TRUE),
             sd(as.numeric(datadmit$cutoff5), na.rm=TRUE),
             sd(as.numeric(datadmit$cutoff6), na.rm=TRUE)
             )

xquality <- c(mean(as.numeric(datadmit$quality1), na.rm=TRUE),
             mean(as.numeric(datadmit$quality2), na.rm=TRUE),
             mean(as.numeric(datadmit$quality3), na.rm=TRUE),
             mean(as.numeric(datadmit$quality4), na.rm=TRUE),
             mean(as.numeric(datadmit$quality5), na.rm=TRUE),
             mean(as.numeric(datadmit$quality6), na.rm=TRUE)
             )

sdquality  <- c(sd(as.numeric(datadmit$quality1), na.rm=TRUE),
             sd(as.numeric(datadmit$quality2), na.rm=TRUE),
             sd(as.numeric(datadmit$quality3), na.rm=TRUE),
             sd(as.numeric(datadmit$quality4), na.rm=TRUE),
             sd(as.numeric(datadmit$quality5), na.rm=TRUE),
             sd(as.numeric(datadmit$quality6), na.rm=TRUE)
             )

xdistance <- c(mean(as.numeric(datadmit$dist1), na.rm=TRUE),
             mean(as.numeric(datadmit$dist2), na.rm=TRUE),
             mean(as.numeric(datadmit$dist3), na.rm=TRUE),
             mean(as.numeric(datadmit$dist4), na.rm=TRUE),
             mean(as.numeric(datadmit$dist5), na.rm=TRUE),
             mean(as.numeric(datadmit$dist6), na.rm=TRUE)
             )

sddistance  <- c(sd(as.numeric(datadmit$dist1), na.rm=TRUE),
             sd(as.numeric(datadmit$dist2), na.rm=TRUE),
             sd(as.numeric(datadmit$dist3), na.rm=TRUE),
             sd(as.numeric(datadmit$dist4), na.rm=TRUE),
             sd(as.numeric(datadmit$dist5), na.rm=TRUE),
             sd(as.numeric(datadmit$dist6), na.rm=TRUE)
             )
result <- rbind(xcutoff, sdcutoff, xquality, sdquality, xdistance, sddistance)
colnames(result) <- c("Choice1", "Choice2", "Choice3", "Choice4", "Choice5", "Choice6")
result
```


```{r discriptive2, echo=TRUE, include=TRUE}
# Divide student into quartile according to her score
summary(datadmit$score)
datadmit$stQr <- NA
datadmit$stQr[which(datadmit$score < 256)] <- 1
datadmit$stQr[which(datadmit$score >= 256 & datadmit$score < 288)] <- 2
datadmit$stQr[which(datadmit$score >= 288 & datadmit$score < 329)] <- 3
datadmit$stQr[which(datadmit$score >= 329)] <- 4

# Calculate descriptive statistics 
rm(quartile, qdata)
quartile <- data.frame("Choice1", "Choice2", "Choice3", "Choice4", "Choice5", "Choice6")
frow <- c(0,0,0,0,0,0)
quartile <- rbind(frow)

for (i in 1:4) {
  qdata <- datadmit[which(datadmit$stQr == i), ]

  qxcutoff <- c(mean(as.numeric(qdata$cutoff1), na.rm=TRUE),
             mean(as.numeric(qdata$cutoff2), na.rm=TRUE),
             mean(as.numeric(qdata$cutoff3), na.rm=TRUE),
             mean(as.numeric(qdata$cutoff4), na.rm=TRUE),
             mean(as.numeric(qdata$cutoff5), na.rm=TRUE),
             mean(as.numeric(qdata$cutoff6), na.rm=TRUE)
             )

  qsdcutoff <- c(sd(as.numeric(qdata$cutoff1), na.rm=TRUE),
             sd(as.numeric(qdata$cutoff2), na.rm=TRUE),
             sd(as.numeric(qdata$cutoff3), na.rm=TRUE),
             sd(as.numeric(qdata$cutoff4), na.rm=TRUE),
             sd(as.numeric(qdata$cutoff5), na.rm=TRUE),
             sd(as.numeric(qdata$cutoff6), na.rm=TRUE)
             )

  qxquality <- c(mean(as.numeric(qdata$quality1), na.rm=TRUE),
             mean(as.numeric(qdata$quality2), na.rm=TRUE),
             mean(as.numeric(qdata$quality3), na.rm=TRUE),
             mean(as.numeric(qdata$quality4), na.rm=TRUE),
             mean(as.numeric(qdata$quality5), na.rm=TRUE),
             mean(as.numeric(qdata$quality6), na.rm=TRUE)
             )

  qsdquality  <- c(sd(as.numeric(qdata$quality1), na.rm=TRUE),
             sd(as.numeric(qdata$quality2), na.rm=TRUE),
             sd(as.numeric(qdata$quality3), na.rm=TRUE),
             sd(as.numeric(qdata$quality4), na.rm=TRUE),
             sd(as.numeric(qdata$quality5), na.rm=TRUE),
             sd(as.numeric(qdata$quality6), na.rm=TRUE)
             )

  qxdistance <- c(mean(as.numeric(qdata$dist1), na.rm=TRUE),
             mean(as.numeric(qdata$dist2), na.rm=TRUE),
             mean(as.numeric(qdata$dist3), na.rm=TRUE),
             mean(as.numeric(qdata$dist4), na.rm=TRUE),
             mean(as.numeric(qdata$dist5), na.rm=TRUE),
             mean(as.numeric(datadmit$dist6), na.rm=TRUE)
             )

  qsddistance  <- c(sd(as.numeric(qdata$dist1), na.rm=TRUE),
             sd(as.numeric(qdata$dist2), na.rm=TRUE),
             sd(as.numeric(qdata$dist3), na.rm=TRUE),
             sd(as.numeric(qdata$dist4), na.rm=TRUE),
             sd(as.numeric(qdata$dist5), na.rm=TRUE),
             sd(as.numeric(qdata$dist6), na.rm=TRUE)
             )
  
 quartile <- rbind(quartile, qxcutoff, qsdcutoff, qxquality, qsdquality, qxdistance, qsddistance)
 rm(qxcutoff, qsdcutoff, qxquality, qsdquality, qxdistance, qsddistance)
}

quartile <- quartile[-1,]
row.names(quartile)<- c("mean.cut.q1", "sd.cut.q1", "mean.qual.q1", "sd.qual.q1","mean.dist.q1","sd.dist.q1",
                          "mean.cut.q2", "sd.cut.q2", "mean.qual.q2", "sd.qual.q2","mean.dist.q2","sd.dist.q2",
                          "mean.cut.q3", "sd.cut.q3", "mean.qual.q3", "sd.qual.q3","mean.dist.q3","sd.dist.q3",
                          "mean.cut.q4", "sd.cut.q4", "mean.qual.q4", "sd.qual.q4","mean.dist.q4","sd.dist.q4"
                          )
colnames(quartile) <- c("Choice1", "Choice2", "Choice3", "Choice4", "Choice5", "Choice6")
#Print result
quartile


```

# Exercise 5 Diversification

``` {r Q5, echo=TRUE, include=TRUE}

  # Create deciles for choices(school,program) by "cutoff" 
  quantile(ssdat$cutoff6, c(.1, .2, .3, .4, .5, .6, .7, .8, .9))
  ssdat$deci <- NA
  ssdat$deci[which(ssdat$cutoff6 < 207)] <- 1
  ssdat$deci[which(ssdat$cutoff6 >= 207 & ssdat$cutoff6 < 212)] <- 2
  ssdat$deci[which(ssdat$cutoff6 >= 212 & ssdat$cutoff6 < 218)] <- 3
  ssdat$deci[which(ssdat$cutoff6 >= 218 & ssdat$cutoff6 < 226)] <- 4
  ssdat$deci[which(ssdat$cutoff6 >= 226 & ssdat$cutoff6 < 240)] <- 5
  ssdat$deci[which(ssdat$cutoff6 >= 240 & ssdat$cutoff6 < 256)] <- 6
  ssdat$deci[which(ssdat$cutoff6 >= 256 & ssdat$cutoff6 < 275)] <- 7
  ssdat$deci[which(ssdat$cutoff6 >= 275 & ssdat$cutoff6 < 298)] <- 8
  ssdat$deci[which(ssdat$cutoff6 >= 298 & ssdat$cutoff6 < 335)] <- 9
  ssdat$deci[which(ssdat$cutoff6 >= 335)] <- 10

  # Assign value of decile to each choice
  ssdat <- ssdat[,-3:-4]
  colnames(ssdat) <- c("schoolcode1","choicepgm1","deci1")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode1","choicepgm1"), all.x = TRUE)

  colnames(ssdat) <- c("schoolcode2","choicepgm2","deci2")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode2","choicepgm2"), all.x = TRUE)

  colnames(ssdat) <- c("schoolcode3","choicepgm3","deci3")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode3","choicepgm3"), all.x = TRUE)
  
  colnames(ssdat) <- c("schoolcode4","choicepgm4","deci4")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode4","choicepgm4"), all.x = TRUE)
  
  colnames(ssdat) <- c("schoolcode5","choicepgm5","deci5")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode5","choicepgm5"), all.x = TRUE)
  
  colnames(ssdat) <- c("schoolcode6","choicepgm6","deci6")
  datadmit <- merge(datadmit,ssdat, by = c("schoolcode6","choicepgm6"), all.x = TRUE)

  # Calculate the number of unique group within the application  
totgroup <- datadmit[,54:59]
totgroup$ngroup <- apply(totgroup, 1, function(x)length(unique(x)) )
datadmit <- merge(datadmit,totgroup, by =c("deci1", "deci2", "deci3", "deci4" , "deci5" , "deci6"), all.x = TRUE)  
summary(datadmit$ngroup)

```


``` {r Q5.2, echo=TRUE, include=TRUE}
  # Calculate the number of unique group within the application by student's score quartile
ngroup1 <- summary(datadmit$ngroup[which(datadmit$stQr ==1)])
ngroup2 <- summary(datadmit$ngroup[which(datadmit$stQr ==2)])
ngroup3 <- summary(datadmit$ngroup[which(datadmit$stQr ==3)])
ngroup4 <- summary(datadmit$ngroup[which(datadmit$stQr ==4)])
sumngroup <- rbind(ngroup1, ngroup2, ngroup3, ngroup4)
sumngroup

```
  